Learning Network Size while Training with ShrinkNets

### 2018-02-09 paper/ICML/evaluation.tex

We assume no prior knowledge on the optimal batch size, learning rate,
$\lambda$ or weight decay ($\lambda_2$). This is why, we randomly sample them
from a range of reasonable values (\gl{should we make them explicit ?}).
Training is done using our library, based on \texttt{PyTorch} [ref], that
support dynamically resized layers. We train the network using gradient descent
and \textit{Adam} optimizer [ref]. We start with the learning rate sampled
randomly and every $5$ epochs of non improvement in validation accuracy we
divide the learning rate by $10$. We stop training after $400$ epochs or when
the learning rate is under $10^{-7}$ whichever comes first. \gl{Should I also
  give the details about the removal strategy we used and the $\gamma$ and
  threshold I used ? because this is clearly getting boring}
For each of the models we trained, we pick the epoch with the best validation
accuracy and report the corresponding testing accuracy. For each model, we also
measure the total size, in number of floating point parameters, excluding the
\textit{Switch Layers} because as we saw in section \gl{REFERENCE\_ME}, we can
get rid of them when training is done.

@@

Our second dataset we will evaluate on is \texttt{COVERTYPE} [ref]. \gl{TODO
  rephrase the description taken from the UCI website} We picked
this one for couple of reasons. First it is simply enough that we can reach good
accuracy with small models. This important because we want to show that
\textit{ShrinkNets} find sizes as good as \textit{Static Networks}, even if we
are sampling the entire space of possible sizes. The second reason is that [ref]
are also doing their evaluation on this dataset, which allow us to compare the
results obtained by the two methods.

@@

\gl{Todo for me: explain how I select the best epoch to get rid of the outliers}

\subsection{Intepretation of the result of random search}

\gl{TODO draw conclusions from the plots}:
\begin{itemize}
  \item Pareto frontier better or as good, even when we sample the entire search
    space
  \item Static NEts are much more spread in terms of size for a given accuracy
    while shrinknets are smarter and always lie close to the frontier (I am
    changing the way I select the best epoch so the outliers in the COVER
    dataset will go away in the next version of the plot)
  \item We reach as good or better accuracies than normal networks
\end{itemize}

@@

Regarding size, the key observation we can make is that size improvenets are
significant for

\subsection{Multi-Target Linear and Multi-Class Logistic regressions}

@@

\subsection{Neuron Removal strategies}

@@

\section{Architectures obtained after convergence}

We sucessfully demonstrated that the architecture \textit{Shrinknets} converge
to make sense both in term of size and performance. And for a given accuracy the
size needed is significantly smaller than when we use the classic heursitc we
commonly use to size convolutional neural networks. It might be an indication
that this strategy is suboptimal and might need to be adjusted. During our
experimentations on simpler datasets like \texttt{MNIST} and
\texttt{FashionMNIST} we observed that even if they have the same number of
classes, input features, and output distribution. For a fixed $\lambda$
\textit{ShrinkNets} converged to considerably bigger networks in the case of
\texttt{FashionMNIST}.
take a look closer to the architectures \textit{ShrinkNets} converge to

>>>>

We assume no prior knowledge on the optimal batch size, learning rate,
$\lambda$ or weight decay ($\lambda_2$). This is why, we randomly sample them
from a range of reasonable values (\gl{should we make them explicit ?}).
Training is done using our library, based on \texttt{PyTorch} [ref], that
support dynamically resized layers. We train the network using gradient descent
and \textit{Adam} optimizer [ref]. We start with the learning rate sampled
randomly and every $5$ epochs of non improvement in validation accuracy we
divide the learning rate by $10$. We stop training after $400$ epochs or when
the learning rate is under $10^{-7}$ whichever comes first. \gl{Should I also
  give the details about the removal strategy we used and the $\gamma$ and
  threshold I used ? because this is clearly getting boring}
For each of the models we trained, we pick the epoch with the best validation
accuracy and report the corresponding testing accuracy. Because of the nature of
our method, it can happen that for network that are aggressively compressed, the
best validation accuracy is obtained early in the training, before the size has
converged. To be sure that accuracy measured corresponds to the final shape and
not the starting shape, we only consider the second half of the training when
picking the best epoch. For each model, we also measure the total size, in
number of floating point parameters, excluding the \textit{Switch Layers}
because as we saw in section \gl{REFERENCE\_ME}, we can get rid of them when
training is done.

@@

Our second dataset we will evaluate on is \texttt{COVERTYPE} [ref]. This dataset
contains $581012$ description of geographical area (elevation, inclination,
etc...) and the goal is to predict the type of forest growing there. We picked
this one for couple of reasons. First it is simple that we can reach good
accuracy with only a few layers. This important because we want to show that
\textit{ShrinkNets} find sizes as good as \textit{Static Networks}, even if we
are sampling the entire space of possible sizes. The second reason is that [ref]
also perform their evaluation on this dataset, which allow us to compare the
results obtained by the two methods.

@@

\subsection{Results of the random search procedure}

On the plot, the Pareto front for the two training methods clearly indicates
that not only \textit{ShrinkNets} find models that are as accurate as
\textit{Static Networks}, but they are more efficient in terms of size. Even
when we sample the entire size space (in the \texttt{COVERTYPE} case),
\textit{ShrinkNets} are better or equally as good as \textit{Static Networks}.
it has two implications. First it reinforces, our observation in [ref] that
showed that the models do not suffer from the non-convexity introduced by the
multiplication by the \textit{Switch Layer}. Secondly it could let us conjecture
that the parametrization from a $\lambda$ (real value) to the size of the
size of the network (vector) is optimal or close to optimal. Indeed, if it was
not the case then eventually a randomly sampled size would have beaten
\textit{ShrinkNets} models. \gl{Too strong ?}

@@

Regarding size, the key observation we can make is that size improvenets are
significant for the \texttt{CIFAR10}. In the range of accuracies we are
interested in, improvements in size go from 4x to 40x. On the \texttt{COVERTYPE}
dataset even if the compression ratio is always above 1, it hardly exceeds 3x,
except for very high accuracy where \textit{ShrinkNets} obtained some
particularly good solutions.

We observe that unlike local sparsity compression based method, our method
translates directly improvement in size to higher bandwidth at inference time.
In situations where inference is already incredibly fast (\texttt{COVERTYPE}
with a batch size of $1$ and \texttt{CIFAR10} with a batch size of $1$ on GPU),
improvements are dominted by noise. However, on machine learning frameworks
more focused on latency it should be possible to measure them.

\subsection{Architectures obtained after convergence}

We sucessfully demonstrated that the architecture \textit{Shrinknets} converge
to make sense both in term of size and performance. And for a given accuracy the
size needed is significantly smaller than when we use the classic heursitc we
commonly use to size convolutional neural networks. It might be an indication
that this strategy is suboptimal and might need to be adjusted. During our
experimentations on simpler datasets like \texttt{MNIST} and
\texttt{FashionMNIST} we observed that even if they have the same number of
classes, input features, and output distribution. For a fixed $\lambda$
\textit{ShrinkNets} converged to considerably bigger networks in the case of
\texttt{FashionMNIST}. This evidence shows that final architecture not only
depends on the output distribution or shape of the data but actually reflects
the dataset (we know that FASHIONMNIST is harder then MNIST)

We provide two examples of architectures learned by \textit{ShrinkNet}. One
for the best test available test accuracy and a slightly underperforming but
significantly (40x smaller that it's equivalent \textit{Static Network}). For
these two architectures we show the size at different time during training to
give a sense how the convergence happen.

\gl{Add the two plots}

\subsection{Multi-Target Linear and Multi-Class Logistic regressions [To be
  moved in the theoretical part]}

@@

\subsection{Neuron Removal strategies [TO be removed]}

@@
